---
title: "Homework4"
author: "wendyxwang"
date: "Sunday, March 01, 2015"
output: html_document
---

#Question
You will have to analyze the RNA-seq data presented in: Henn, A. D. et al. High-resolution temporal response patterns to influenza vaccine reveal a distinct human plasma cell gene signature. Scientific Reports 3, 2327 (2013).

Get the data from GEO. Please look at the class lecture slides as we've done it already
Use voom and limma to find genes that are differentially expressed at each time point compared to baseline (day 0). Use an FDR cutoff of 0.01. Display your results using pheatmap showing the log fold-change of the differentially expressed genes grouped by time point.
Perform a GSEA analysis using camera and the MSigDB Reactome pathway gene signatures. Display your results using pheatmap, again group by timepoint. This is similar to what we've done in class.

#Answers
Set up general options
```{r}
library("knitr")
opts_chunk$set(tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=60), cache=TRUE, messages=FALSE)

#set working directory
setwd("E:/Course2015Winter/BIOST578/RStudio clone/HW4_Xiaoliang_Wang")
```
Set up libraries
```{r}
library(data.table)
library(ggplot2)
library(limma)
library(edgeR)
library(GEOquery)
library(pheatmap)
```

#1. Get the data from GEO
```{r}
#This chunck of codes are directly copied from GSEA slides
gd <- getGEO("GSE45735", destdir = "Data/GEO/")
pd <- pData(gd[[1]])
getGEOSuppFiles("GSE45735", makeDirectory=FALSE, baseDir = "Data/GEO/")

# Note the regular expression to grep file names
files <- list.files(path = "Data/GEO/", pattern = "GSE45735_T.*.gz", full.names = TRUE)

# Read in gzip-compressed, tab-delimited files
file_list <- lapply(files, read.table, sep='\t', header=TRUE)

# Subset to only those rows where Gene contains only non-space characters
# This addresses problems with T14 file containing 28 invalid rows at end of file
file_list <- lapply(file_list, function(file_list)subset(file_list, grepl('^[^[:space:]]+$', Gene)))
```

#2. Find genes that differentially expressed compared to baseline

#3. Perform a GSEA analysis using camera and the MSigDB Reactome pathway gene signatures
